A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-07-25 papers/paper1/ms.tex
Reran the data with normalized lightcurves and recreated the figures

\begin{figure}[!htb]
  \centering
  \includegraphics[scale=0.5]{Amplitude Comparison Mask.png}
  \caption{The mask showing how we determined which points were outliers.}
\end{figure}
\FloatBarrier

@@

@@

As seen in the figure below, the Kepler data are, on average, around 70 times larger than TESS's.

\begin{figure}[!htb]
  \centering
  \includegraphics[scale=0.42]{Amplitude vs. Rotation for Kepler and TESS.png}
  \caption{Effect size for starspot contrast as seen in modulation amplitude versus period ($P_{\mathrm{rot}}$ [days]). The black points are the locus of spotted stars in the Kepler as measured by for late K dwarfs. The red points are the same stars, but measured with the TESS mission. The blue and green dashed lines represents the average amplitudes for all plotted stars for both Kepler and TESS, approximately 9350 and 130, respectively.}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}[!htb]
  \centering
  \includegraphics[scale=0.5]{Amplitude Comparison Mask.png}
  \caption{The mask showing how we determined which points to keep and which ones were outliers.}
\end{figure}
\FloatBarrier

@@

% \begin{figure}[hbt!]
%   \includegraphics[width=0.95\textwidth]{figures/contrast_spectrum2.pdf}
%   \caption{Illustration of starspot contrast as seen in \tess\ and \kepler. The red shaded spectrum illustrates the contrast for an M0V spectral type for a choice of spot and ambient photospheric temperatures. The thick blue left-most curve illustrates the \kepler\ passband, the thick green line to its right illustrates the \tess\ passband centered near 850 nm.  A lower number means darker spots.}
%   \label{fig:filtercurve}
% \end{figure}

@@

As seen in the figure below, the TESS data are, on average, around 175\% larger than Kepler.

\begin{figure}[!htb]
  \centering
  \includegraphics[scale=0.42]{Amplitude vs. Rotation for Kepler and TESS.png}
  \caption{Effect size for starspot contrast as seen in modulation amplitude versus period ($P_{\mathrm{rot}}$ [days]). The black points are the locus of spotted stars in the Kepler as measured by for late K dwarfs. The red points are the same stars, but measured with the TESS mission. The blue and green dashed lines represents the average amplitudes for all plotted stars for both Kepler and TESS, approximately 3.98\% and 6.94\%, respectively.}
\end{figure}
\FloatBarrier
